\chapter{Literature}
	\newpage
	\section{General Literature Trivia}
		\subsection{Opening Lines}
		These are some of the most famous opening lines, and their sources.
		\vspace{0.15in}
		
		\begin{longtable}{|p{3in}| p{1.4in}| p{1.4in}|}
		\hline
		\textbf{Opening Line} & \textbf{Work} & \textbf{Author} \\
		\hline
		
			Many years later, as he faced the firing squad, Colonel Aureliano Buend\`ia was to remember that distant afternoon when his father took him to discover ice. & 100 Years of Solitude & Gabriel Garcia Marquez \\
			
			\hline
		
			It was a bright cold day in April, and the clocks were striking thirteen. & 1984 & George Orwell \\
			\hline
			All happy families are alike; each unhappy family is unhappy in its own way. & Anna Karenina & Leo Tolstoy \\
			\hline
			IF you really want to hear about it, the first thing you probably want to know is where I was born, and what my childhood was like...& The Catcher in the Rye & J. D. Salinger \\	
			\hline
			``Where's Papa going with that ax?'' asked Fern to her mother as they were setting the table for breakfast. & Charlotte's Web & E. B White \\			
			\hline
			In my younger years my father gave me some advice that I've been turning over in my mind ever since. & The Great Gatsby & F. Scott Fitzgerald \\
			\hline
			It was a pleasure to burn. & Fahrenheit 451 & Ray Bradbury \\
			\hline
			We slept in what had once been the gymnasium. & The Handmaid's Tale & Margaret Atwood \\
			
			\hline
			In a hole in the ground there lived a hobbit.  & The Hobbit & J. R. R. Tolkien \\	
			\hline
			Jewel and I come up from the field, following the path in single file. & As I Lay Dying & William Faulkner \\
			
			\hline
			There was no possibility of taking a walk that day. & Jane Eyre & Charlotte Bront\"e \\
			\hline
			When  he was nearly thirteen, my brother Jem got his arm badly broken at the elbow.  & To Kill a Mockingbird & Harper Lee \\
			\hline
			My suffering left me sad a gloomy.  & Life of Pi & Yann Martel \\
			\hline
			Lolita, light of my life, fire of my loins. My sin, my soul.  & Lolita & Vladimir Nabokov \\
			\hline
			The week before I left my family and Florida and the rest of my minor life to go to boarding school in Alabama, my mother insisted on throwing me a going-away party. & Looking for Alaska & John Green \\
			
			\hline
			As Gregor Samsa awoke one morning from uneasy dreams he found himself transformed in his bed into a monstrous vermin & The Metamorphosis & Franz Kafka \\
			\hline
			Call me Ishmael & Moby Dick &Herman Melville \\
			\hline
			They're out there.  Black boys in white suits up before me to commit sex acts in the hall and get it mopped up before I can catch them. & One flew over the Cuckoo's Nest & Ken Kesey \\ 
			\hline
			All children, except one, grow up. & Peter Pan & J.M. Barrie \\
			\hline
			It is a truth universally acknowledged, that a single man in possession of a good fortune, must be in want of a wife. & Pride and Prejudice & Jane Austin \\
			\hline
			In our family, there was no clear line between religion and fly-fishing. & A River runs through it & Norman Maclean \\
			\hline
			All this happened, more or less.  & Slaughterhouse-Five & Kurt Vonnegut \\
			\hline
			Mother died today. & The Stranger & Albert Camus \\
			\hline
			It was the best of times, it was the worst of times... & A Tale of Two Cities & Charles Dickens \\
			\hline
			Stately, plump Buck Mulligan came from the stairhead, bearing a bowl of lather on which a mirror and a razor lay crossed. & Ulysses & James Joyce\\
			\hline
			
			
			
			
		\end{longtable}
	
	\section{American Literature}
		\subsection{Fiction}
		\subsubsection{William Faulkner}
			\paragraph{A Rose for Emily}
			\paragraph{As I Lay Dying}
			\paragraph{Barn Burning}
			\paragraph{Light in August}
			\paragraph{The Hamlet}
			
		\subsubsection{F. Scott Fitzgerald}
			\paragraph{The Great Gatsby}
			 \paragraph{Tender is the Night} - The title is taken from the poem "Ode to a Nightingale" by John Keats. 
			 \paragraph{This Side of Paradise}
			 
			
			\subsubsection{John Greene}
			\paragraph{Looking For Alaska}
			
			\subsubsection{Herman Melville}
			\paragraph{Moby Dick}
			
			
			\subsubsection{J. D. Salinger}
			\paragraph{The Catcher in the Rye}
			
			
			\subsubsection{Kurt Vonnegut}
			\paragraph{Slaughterhouse-Five}			

			

			

			
			
		\subsection{Nonfiction}
			\subsubsection{Silent Spring}
		\subsection{Poetry}

			

		
	\section{European Literature}
		\subsection{Fiction}
			\subsection{1984}
			\subsubsection{Animal Farm}
			\subsubsection{Ulysses}
			
		\subsection{Nonfiction}
			\subsubsection{Mutiny on the Bounty}




\newpage
		\subsection{Poetry}
		
		\subsubsection{William Blake}
		\label{WilliamBlakeLit} This section is about William Blake's Literature.  To learn about Artwork by William Blake, see \ref{WilliamBlakeArt} on \cpageref{WilliamBlakeArt}
			\paragraph{The Tyger}
			\paragraph{London}
			\paragraph{The Lamb}
		\subsubsection{Shakespeare} \label{Shakespeare-Poetry} For Shakespere's Plays, see \ref{Shakespeare-Play} on \cpageref{Shakespeare-Play}
		
	\newpage
	\section{Religious Literature}
		\subsection{Abrahamic Religions}
			\subsubsection{Jewish}
				\paragraph{Bible - Old Testamant)} \label{Old Testamant}
				The Jewish bible (and the Old Testamant for Christians, also recognized by Muslims) is divided into three main sections:
				\begin{enumerate}
					\item The Five Books of Moses (Torah or Chumash)
					\begin{enumerate}
						\item Genesis - Creation, Adam and Eve, Cain and Abel, Seth, Noah, Abraham, Isaac, Jacob.  
						\item Exodus - The departure of Israelites from Egypt.  Moses, Aaron.  Water from the rock, quail, and manna.
						\item Leviticus - Many priestly and ritual laws. 
						\item Numbers - a detailed census of the Israelite in the desert; 
						\item Deuteronomy - the Israelites wander in the desert, and finally come to the promised land.
						
					\end{enumerate}
					\item The Eight Books of the Prophets (Neviim)
						\begin{enumerate}
							\item Joshua - The battle of Jericho and the Conquest of Canaan. 
							\item Judges - The first rulers of Israel.
							\item Samuel - The rise of King David. 
							\item Kings David dies, solomon builds a temple. Israel splits into a Northern and Southern Kingdom. 
							\item Isaiah - Tells of the coming of a prophet; Cyrus of Persia is mentioned as the Annoointed one of God. 
							\item Jeremiah - Written in the final years before the Babylonian exile.
							\item Ezekial (Spelled Ezekiel by most English-speaking Christians).  Apocolyptic Literature. 
							\item The Twelve (minor prophets) Trei-Assar 
						\end{enumerate}
					\item The Eleven Books of the Writings (Kesuvim)
						\begin{enumerate}
							\item Psalms - Tehilim
							\item Proverbs - Mishlei
							\item Job - Iyov
							\item Song of Songs - Shir HaShirim
							\item Ruth - Rus
							\item Lamentations - Eicha
							\item Ecclesiastes - Koheles
							\item Esther
							\item Daniel - Doniel
							\item Ezra/Nehemia
							\item Chronicles - Divrei Hayamim 
						\end{enumerate}
					
				\end{enumerate}

				\paragraph{Talmud}
				
			\subsubsection{Christian}
			The Christian Bible is divided into two parts:
			\begin{enumerate}
				\item The Old Testament is shared with the Jewish and Muslim religions. See \ref{Old Testamant} on page \pageref{Old Testamant}
				
				\item The New Testamant
			\end{enumerate}

					

			\subsubsection{Muslim}
				\paragraph{Koran}
				
		\subsection{Eastern Religions}
			\subsubsection{Hindu}
			\subsubsection{Buddhist}

		
		
		\subsection{Talmud}
		\subsubsection{title}
	\section{World Literature}